### 2012-02-02 paper.tex
Added content and a figure to the experimental section. Moved a reference from the complete list to the actual reference list

\noindent \normalsize{The abstract should be a single paragraph which summarises the content of the article. Any references in the abstract should be written out in full \textit{e.g.} [Surname \textit{et al., Journal Title}, 2000, \textbf{35}, 3523].}
\vspace{0.5cm}
 \end{@twocolumnfalse}
  ]

@@

It has previously been shown (REF) that CO oxidation will show oscillatory behavior on single crystals on palladium \cite{Hendriksen2010} attributed to a cycle of surface oxide formation, oxide roughening and bare metal surface. CO oxidation oscillations on has also been observed on thin-films \cite{Lund2000} and in macroscopic flow reactors \cite{Singh2010} but never on size selected platinum nanoparticles at atmospheric pressures for prolonged periods of time.

\section{Experimental Methods}
\subsection{$\mu$-reactors}
Reaction data was performed in silicon-based microreactors developed in-house \cite{Henriksen2009}. The reactor consists of a two inlets, a long mixing zone for the reaction gases to allow for diffusional mixing, an outlet, a reactor volume of $240\,$nL and a $5.4\,\mu$m wide capillary used for probing the gases from the reactor volume. The reactor is sealed from atmosphere by anodic bonding of a pyrex lid to the silicon reactor is able to operate at a pressure range of 0-2.5\,bar. The reaction gases is supplied through flow controllers capable of controlling flow in the range of a 1-10 mL/min. The capillary flow fed into a quadropole mass-spectrometer while any extra gas from the inlets are passed through the outlet connected to a pressure controller to control the reactor pressure. The design ensures that all gas exposed to the catalyst under investigation is measured by the mass spectrometer ensuring a high sensitivity of the device. When an evacuated microreactor is mounted, the base pressure of the mass spectrometer chamber is $\sim5\times10^{-9}\,$mbar and when operating at $1\,$bar in the reactor the pressure is $\sim5\times10^{-7}\,$mbar.

The reactor is heated by joule heating of platinum strip evaporated on the backside of the reactor volume. The introduction of two additional contacts on the backside of the reactor allows for 4 wire measurements of the resistance of the platinum strip using it as a RTD for temperature measurement of the reactor volume.

@@

\section{Results}
The experiments was carried out ....

The period of the oscillations ranges from a few seconds (the time-constant of the reactor) up to more than an hour. A typical slow is oscillation is seen in figure~\ref{fgr:full_oscillation} where we see the typical pattern going from almost no activity slowly up towards $\sim$50\% conversion at which point the sample light off to full conversion almost instantiously where after a short peiod of time the sample again de-activates.
% an example of a two-column figure, remember that the graphics should be included where it is first referenced
\begin{figure*}
  \centering
  \includegraphics[width=17cm]{single_full_oscillation.png}
  \caption{A full oscillation first showing a steep ignition of the sample followed by an almost imidiately de-activation of the sample. For the next 65 minutes the sample slowly recovers activity until it again lights off completely.}
  \label{fgr:full_oscillation}
\end{figure*}

If a sample is leaved for long periods of time, it keeps performing sustained oscillations, but with longer and longer periods. In the beginning the period is very stable and sligtly increasing but after a few days, the periods becomes more and more noisy although still maintaining the trend of longer and longer periods. Figure~\ref{fgr:full_oscillation} shows a summary of the periods of a sample oscillating for 4 days. 
% an example of a single-column figure, remember that the graphics should be included where it is first referenced
\begin{figure}[h]
\centering
  \includegraphics[width=9cm]{summary_of_long_measurement.png}
  \caption{Summary of a sample oscillating under constant temperature, pressure and reactant composition. The sample went through a total of 439 oscillations in 4 days.}
  \label{fgr:long_measurement}
\end{figure}

Extracts of the mass-spectrometry from the very beginning, the middle and towards the end of the experiments is shown in figure~\ref{fgr:extracts}, it is evident that the oscillations are getting more and more irregular as times goes on, towards the end, it is also clearly visible how the smaller oscillations are taking place at a much higher frequency than the full on-off cycles, which is most likely the explanation for the increasing scatter in the period summary.
% an example of a two-column figure, remember that the graphics should be included where it is first referenced
\begin{figure}[h]
  \centering
  \includegraphics[width=9cm]{extracts_from_very_long_oscillation.png}
  \caption{Extracts from the 4 day long experiment.}
  \label{fgr:extracts}
\end{figure}

Several different samples deposited at various diffent sizes and amounts all show the oscillating bahaviour. Repeatability is high regarding running long experiments on a single sample, but very low from sample to sample.

\section{Discussion}
Due to long timescales involved which are much larger than any typically orcurring timescales for such a small system, there can be little doubt that this phenomenon involves some kind of reaction involving the bulk of the nano particles.

@@

\section{Equations}

Equations can be typeset inline \textit{e.g.} $ y = mx + c$ or displayed with and without numbers:

 \[ A = \pi r^2 \]

\begin{equation}
  \frac{\mathrm{\gamma}}{\mathrm{\epsilon}x} r^2 = 2r
\end{equation}

\section{Graphics and tables}
\subsection{Graphics}
Graphics should be inserted on the page where they are first mentioned (unless they are equations, which appear in the flow of the text).

\subsection{Tables}
Tables typeset in RSC house style do not include vertical lines. Table footnote symbols are lower-case italic letters and are typeset at the bottom of the table. Table captions do not end in a full point.

\begin{table}[h]
\small
  \caption{\ An example of a caption to accompany a table}
  \label{tbl:example}
  \begin{tabular*}{0.5\textwidth}{@{\extracolsep{\fill}}lll}
    \hline
    Header one/units & Header two & Header three \\
    \hline
    1 & 2 & 3 \\
    4 & 5 & 6 \\
    7 & 8 & 9 \\
    10 & 11 & 12 \\
    \hline
  \end{tabular*}
\end{table}

Adding notes to tables can be complicated.  Perhaps the easiest
method is to generate these manually.

@@

You can also put lists into the text. You can have bulleted or numbered lists of almost any kind. 
The \texttt{mhchem} package can also be used so
that formulae are easy to input: \texttt{\textbackslash ce\{H2SO4\}} gives \ce{H2SO4}.

\section{Conclusions}
The conclusions section should come at the end of article. For the reference section, the style file rsc.bst can be used to generate the correct reference style.\footnote[4]{Footnotes should appear here. These might include comments relevant to but not central to the matter under discussion, limited experimental and spectral data, and crystallographic data.}
 %For footnotes in the main text of the article please number the footnotes to avoid duplicate symbols. e.g.  \footnote[num]{your text} the corresponding author \ast counts as footnote 1, ESI as footnote 2, e.g. if there is no ESI, please start at [num]=[2], if ESI is cited in the title please start at [num]=[3] etc. Please also cite the ESI within the main body of the text using \dag.

>>>>

\noindent \normalsize{High-quality mass spectrometry of the oscillatory behaviour of CO oxidation on supported Pt-nanoparticles is presented. It is demonstrated that the oscillations can continue self-sustained for several days. It is demonstrated that the oscillations exhibits a well defined frequency which is slowly developing towards lower freqeuncy.}
%Any references in the abstract should be written out in full \textit{e.g.} [Surname \textit{et al., Journal Title}, 2000, \textbf{35}, 3523].
\vspace{0.5cm}
 \end{@twocolumnfalse}
  ]

@@

It has previously been shown that CO oxidation will show oscillatory behavior on single crystals on palladium \cite{Hendriksen2010} attributed to a cycle of surface oxide formation, oxide roughening and bare metal surface. CO oxidation oscillations on has also been observed on thin-films \cite{Lund2000} and in macroscopic flow reactors \cite{Singh2010} but never on size selected platinum nanoparticles at atmospheric pressures for prolonged periods of time.

\section{Experimental Methods}
\subsection{$\mu$-reactors}
Reaction data was performed in silicon-based microreactors developed in-house \cite{Henriksen2009}. The reactor consists of two inlets, a long mixing zone for the reaction gases to allow for diffusional mixing, an outlet, a reactor volume of $240\,$nL and a $5.4\,\mu$m wide capillary used for probing the gases from the reactor volume. The reactor is sealed from atmosphere by anodic bonding a pyrex lid to the silicon reactor, it is able to operate at a pressure range of 0-2.5\,bar. The reaction gases is supplied through flow controllers capable of controlling flow in the range of 0-10 mL/min. The capillary flow is fed into a quadropole mass-spectrometer while any extra gas from the inlets are passed directly through to the outlet connected to a pressure controller to control the reactor pressure. The design ensures that all gas exposed to the catalyst under investigation is measured by the mass spectrometer ensuring a high sensitivity of the device. When an evacuated microreactor is mounted, the base pressure of the mass spectrometer chamber is $\sim5\times10^{-9}\,$mbar and when operating at $1\,$bar in the reactor the pressure is $\sim5\times10^{-7}\,$mbar.

The reactor is heated by joule heating of platinum strip evaporated on the backside of the reactor volume. The introduction of two additional contacts on the backside of the reactor allows for 4 wire measurements of the resistance of the platinum strip using it as a RTD for temperature measurement of the reactor volume. An external thermocouple acts as room-temperature calibration of the RTD as well as sanity check of the RTD measurement doing operation.

The system is fully automized, allowing for measurements of several days without human intervention. This allows for very self-consistent measurements of many samples.

A typical oscillation maesurement is done by mounting a sample in setup directly after cluster deposition and anodic bonding. A typical measurement will involve an initial light-off CO-oxidation measurement, where the temperature is slowly increased up until the sample ignites and achieves full conversion of the CO. At the typical conditions (O:CO ratio of typically $\sim13$ and Pt-coverage of $\sim0.1\%$) lighoff happens around 180$^\circ$C, the ramp is typically continued up to 260$^\circ$C whereafter the temperature is lowered at the same rate as the heating (typically 3$^\circ$C/min). A typical initial treatment is seen in figurefigure~\ref{fgr:initial_treatment} Often the sample will show oscillations either directly upon lightoff or on the falling temperature ramp. Sustained oscillations is then achieved by following the same heathing ramp up to a fixed temperature and then the temperature is kept constant for the remaing period of the measurement.
\begin{figure}[h]
\centering
  \includegraphics[width=9cm]{initial_treatment.png}
  \caption{A typical example of the initial treatment of a new sample.}
  \label{fgr:initial_treatment}
\end{figure}

@@

\section{Results}
During the experiments we have tried a large number of samples, and it is evident that the oscillation phenomenon is rather easy to reproduce. In agreement with litterature\cite{Singh2010} (FLERE REFS), we find that a very high oxygen concentration (on the order of 13:1) is needed to get the oscillations running, most likely because the much higher sticking coefficient of CO would otherwise result in a completely CO poisoned sample doing the low-reactivity region of the cycle. In our setup we also found that we need a very low coverage on the order 0.1\% of nano-particles to achive consistent oscillations. This is for sure an artifact of our very small reactor, since other groups have seen oscillations on both extended thin-films \cite{Singh2010} as well as on single crystals (REF TIL FRENKEN).

The period of the oscillations ranges from a few seconds (the time-constant of the reactor) up to more than an hour. A slow is oscillation is seen in figure~\ref{fgr:full_oscillation} where we see the typical pattern going from almost no activity slowly up towards $\sim$50\% conversion at which point the sample light off to full conversion almost instantiously where after a short peiod of time the sample again de-activates.
% an example of a two-column figure, remember that the graphics should be included where it is first referenced
\begin{figure*}
  \centering
  \includegraphics[width=17cm]{single_full_oscillation.png}
  \caption{A full oscillation first showing a steep ignition of the sample followed by an almost imidiately de-activation of the sample. For the next 65 minutes the sample slowly recovers activity until it again lights off completely.}
  \label{fgr:full_oscillation}
\end{figure*}

If a sample is leaved at constant temperature for long periods of time, it keeps performing sustained oscillations, but with longer and longer periods. In the beginning the period is very stable and sligtly increasing but after a few days, the periods becomes more and more noisy although still maintaining the trend of longer and longer periods. Figure~\ref{fgr:full_oscillation} shows a summary of the periods of a sample oscillating for 4 days. 
% an example of a single-column figure, remember that the graphics should be included where it is first referenced
\begin{figure}[h]
\centering
  \includegraphics[width=9cm]{summary_of_long_measurement.png}
  \caption{Summary of a sample oscillating under constant temperature, pressure and reactant composition. The sample went through a total of 439 oscillations in 4 days.}
  \label{fgr:long_measurement}
\end{figure}

Extracts of the mass-spectrometry from the very beginning, the middle and towards the end of the experiments is shown in figure~\ref{fgr:extracts}, it is evident that the oscillations are getting more and more irregular as times goes on. Towards the end, it is also clearly visible how  oscillations with smaller amplitude are taking place at a much higher frequency than the full on-off cycles, which is most likely the explanation for the increasing scatter in the period summary, sometimes the smaller oscillations will trigger a full switch, and sometimes it will not, thus introducing more short-period oscillations despite the trend of slower and slower oscillations.
% an example of a two-column figure, remember that the graphics should be included where it is first referenced
\begin{figure}[h]
  \centering
  \includegraphics[width=9cm]{extracts_from_very_long_oscillation.png}
  \caption{Extracts from the 4 day long experiment.}
  \label{fgr:extracts}
\end{figure}

\section{Discussion}
Due to long timescales involved which are much larger than any typically orcurring timescales for such a small system, there can be little doubt that this phenomenon involves some kind of reaction involving the bulk of the nano particles. Due to the nature of our reactor system, it is almost impossible to gain extra insight through traditional surface science techniques, but it has eaelier been showed that in other experimental setups, it is possible to apply both SPM microscopy \cite{Hendriksen2005} as well as infrared spectroscopy \cite{Carlsson2006}.

@@

%\section{Equations}

%Equations can be typeset inline \textit{e.g.} $ y = mx + c$ or displayed with and without numbers:

% \[ A = \pi r^2 \]

%\begin{equation}
%  \frac{\mathrm{\gamma}}{\mathrm{\epsilon}x} r^2 = 2r
%\end{equation}

%\section{Graphics and tables}
%\subsection{Graphics}
%Graphics should be inserted on the page where they are first mentioned (unless they are equations, which appear in the flow of the text).

%\subsection{Tables}
%Tables typeset in RSC house style do not include vertical lines. Table footnote symbols are lower-case italic letters and are typeset at the bottom of the table. Table captions do not end in a full point.

%\begin{table}[h]
%\small
%  \caption{\ An example of a caption to accompany a table}
%  \label{tbl:example}
%  \begin{tabular*}{0.5\textwidth}{@{\extracolsep{\fill}}lll}
%    \hline
%    Header one/units & Header two & Header three \\
%    \hline
%    1 & 2 & 3 \\
%    4 & 5 & 6 \\
%    7 & 8 & 9 \\
%    10 & 11 & 12 \\
%    \hline
%  \end{tabular*}
%\end{table}

%Adding notes to tables can be complicated.  Perhaps the easiest
%method is to generate these manually.

@@

%You can also put lists into the text. You can have bulleted or numbered lists of almost any kind. 
%The \texttt{mhchem} package can also be used so
%that formulae are easy to input: \texttt{\textbackslash ce\{H2SO4\}} gives \ce{H2SO4}.

%\section{Conclusions}
%The conclusions section should come at the end of article. For the reference section, the style file rsc.bst can be used to generate the correct reference style.\footnote[4]{Footnotes should appear here. These might include comments relevant to but not central to the matter under discussion, limited experimental and spectral data, and crystallographic data.}
 %For footnotes in the main text of the article please number the footnotes to avoid duplicate symbols. e.g.  \footnote[num]{your text} the corresponding author \ast counts as footnote 1, ESI as footnote 2, e.g. if there is no ESI, please start at [num]=[2], if ESI is cited in the title please start at [num]=[3] etc. Please also cite the ESI within the main body of the text using \dag.
